---
title: "Assignment 2 Starter Analysis"
format: html
---

## Setup

```{r}
#| message: false
#| warning: false
library(readr)     
library(dplyr)
```

## Load Data

```{r}
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
```

## Inspect

```{r}
dim(nhanes)
names(nhanes)
glimpse(nhanes)
colSums(is.na(nhanes))
```

## Summarize

Replace this example with your own summary if you choose a different question.

```{r}
#I needed to figure out how to filter the data to deal with missing #values using the muatate function. I used AI to check if muatate was #the right function to use. There was also some auto correct with AI #when it came to writing the code. I also needed to check if I was using #filter() correcting and I checked that with AI. I also used AI to #understand what .groups= "drops" meant for and what that line of code #did. 


bmi_summary <- nhanes|>
mutate(has_bmi_income=!is.na(BMI) & !is.na(IncomeGroup))|>
filter(has_bmi_income)|>
group_by(IncomeGroup)|>
summarise(
  n=n(),
  mean_bmi = mean(BMI),
  .groups = "drop"
)
bmi_summary
```

## Function

```{r}
#changed function(values) so i could understand what we are trying to do #used AI to audit and make sure this was correct for this task number
mean_and_sd_function <-function(values){
  tibble(
    mean=mean(values,na.rm=TRUE),
    sd=sd(values,na.rm=TRUE)
  )
}

mean_and_sd_function(nhanes$BMI)
```

## Save Output

```{r}
dir.create("assignments/assignment02-r-with-ai/submission/output", recursive = TRUE, showWarnings = FALSE)
write_csv(bmi_summary, "assignments/assignment02-r-with-ai/submission/output/summary_table.csv")
```

## AI Audit Note

#For this assignment, AI was used to check if I was doing the code correctly and was also used so i could look up what certain code lines meant that was already apart of the starter analysis. For the mutate section needed to change , to & to handle the NA values which AI told me to switch. .groups told me what that did. for function values I wanted to change it so i could write something that helped with my understadning. 